Using cosmic variance to constrain the dark matter halo mass of Lyman-alpha emitting galaxies at $z$=3.1

### 2013-06-06 paper/ms.tex
new plots

@@

%\begin{figure*}
%\begin{center}
%\includegraphics[width=0.46\linewidth,angle=0]{./plots/random_large_correlation_selected_models.pdf}
%\hspace{5mm}
%\includegraphics[width=0.46\linewidth,angle=0]{./plots/random_full_correlation_selected_models.pdf}
%\end{center} 
%\caption{ mean ACFs   and their correponding standard deviation (error
%  bars)  of some selected models in different mass ranges over the 7
%  subfields of the SSA22 field (left) and the entire 12 field sample
%  (rigth) using the  random
%  configuration. \label{figure:correlation_random} }   
%\end{figure*}

>>>>

In figure \ref{fig:restriction_mock_and_f_occ_corr} we present the prefered
models in the planes $M_{\rm min}-M_{\rm  max}$ and $M_{\rmmin}-f_{\rm occ}$
for the {\tt match} method after applying the observational constraints 
in the occupation fraction and the ACF.

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/mmin_vs_mmax.pdf}
\end{center}
\caption{Best models when both the constraints on the maximal number
  of  consistent mocks and the occupation  fraction $f_{\rm occ}\leq
  0.2$ are included. \label{fig:restriction_mock_and_f_occ_corr}} 
\end{figure*} 
%\begin{figure*}
%\begin{center}
%\includegraphics[width=0.46\linewidth,angle=0]{./plots/random_large_correlation_selected_models.pdf}
%\hspace{5mm}
%\includegraphics[width=0.46\linewidth,angle=0]{./plots/random_full_correlation_selected_models.pdf}
%\end{center} 
%\caption{ mean ACFs   and their correponding standard deviation (error
%  bars)  of some selected models in different mass ranges over the 7
%  subfields of the SSA22 field (left) and the entire 12 field sample
%  (rigth) using the  random
%  configuration. \label{figure:correlation_random} }   
%\end{figure*}
